Picky with peakpicking: assessing chromatographic peak quality with simple

### 2023-08-02 manuscript/manuscript.Rmd
Adding country information to author affiliations

---
title: 'Picky with peakpicking: assessing chromatographic peak quality with simple
  metrics in metabolomics'
author: 
  - William Kumler$^1$
  - Bryna J. Hazelton$^{2, 3}$
  - Anitra E. Ingalls$^1$*
  - "Corresponding author email address: aingalls@uw.edu"
  - "Author affiliations: $^1$University of Washington, School of Oceanography, Seattle, WA 98195, USA; $^2$University of Washington, eScience Institute, Seattle, WA 98195, USA; $^3$University of Washington, Department of Physics, Seattle, WA 98195, USA"
output:
  word_document:
    reference_docx: template.docx
bibliography: refs.bib
csl: bmc-bioinformatics.csl
---

>>>>

---
title: 'Picky with peakpicking: assessing chromatographic peak quality with simple
  metrics in metabolomics'
author: 
  - William Kumler$^1$
  - Bryna J. Hazelton$^{2, 3}$
  - Anitra E. Ingalls$^1$*
  - "Corresponding author email address: aingalls@uw.edu"
  - "Author affiliations: $^1$University of Washington, School of Oceanography, Seattle, WA 98195, United States; $^2$University of Washington, eScience Institute, Seattle, WA 98195, United States; $^3$University of Washington, Department of Physics, Seattle, WA 98195, United States"
output:
  word_document:
    reference_docx: template.docx
bibliography: refs.bib
csl: bmc-bioinformatics.csl
---
